\cvsection{Experience}

% In silence
% DAJ

\begin{cventries}

\cventry
  {Deputy Director \& Senior Research Scientist}
  {\href{https://www.crosslabs.org/}{Cross Labs, Cross Compass Ltd.}}
  {Kyoto, Japan}
  {July 2024 - Present}
  {
    \begin{cvitems}
      \item {Provides strategic vision and operational leadership across Cross Labs research and outreach initiatives.}
      \item {Aligns research initiatives with Cross Compass business strategy, driving value through the coordination of strategic research partnerships with external industry collaborators.}
      \item {Served as Vice Chair and lead organizer of \href{https://2025.alife.org}{\textbf{ALIFE 2025: Ciphers of Life}}, a global conference on artificial life.}
      \item {Oversees hiring, project alignment, and international partnerships with academia and industry.}
      \item {Supports interdisciplinary teams working at the intersection of AI, biology, cognition, and information theory.}
      \item {Develops theoretical frameworks for constraint–function loops, embedded agency, and open-ended evolution.}
    \end{cvitems}
  }

\cvsubposition
  {Research Scientist}
  {Oct 2022 - July 2024}
  {
    \begin{cvitems}
      \item {Led theoretical research on emergent computation, astrobiology, artificial life, and multi-agent systems.}
      \item {Developed models linking constraint dynamics to functional emergence in biological and computational systems.}
      \item {Designed and led a lab-wide internship program hosting over 15 interns (2023–2024), fostering cross-disciplinary mentorship and research experience.}
      \item {Coordinated and hosted the \href{https://www.youtube.com/watch?v=bgB8e3Goa2o&list=PLODRPaSTLJCdZDKuvfFFLRztSUYWQ2dkD}{\textbf{Cross Roads}} speaker series and the \href{https://www.youtube.com/watch?v=u0RD11jJcVs&list=PLODRPaSTLJCeDbLrnbfvX_rMgPrJwCu6t}{\textbf{On My Mind}} podcast, showcasing leading thinkers in fields related to intelligence.}
      \item {Led planning and program development for the Cross Labs Spring Workshops in both 2023 and 2024, integrating art, science, and industry collaborations.}
    \end{cvitems}
  }

\cventry
  {Science Fiction Writing}
  {Independent Consultant}
  {Remote}
  {Sep 2022 - May 2025}
  {
    \begin{cvitems}
      \item {Collaborated with published science fiction authors to provide scientific consulting and creative support.}
      \item {Designed speculative technologies, worldbuilding architectures, and consistent physics-based systems.}
      \item {Offered expertise across fields including biology, computation, astrobiology, and complex systems.}
    \end{cvitems}
  }

\cventry
    {Co-founder \& CTO}
    {\href{https://www.pro-phound.com/}{ProPhounD}}
    {Virtual}
    {January 2021 - Dec 2025}
    {
    \begin{cvitems}
      \item {Led technological strategy for low-barrier community-driven support for PhDs exploring career options.}
      \item {Participated in global startup incubators and development programs focused on entrepreneurship and scientific innovation.}
      \item {Shaped business strategy and guided technical development from prototype to pilot deployment.}
      \item {Built and sustained collaborations with academic partners, clinicians, and international technology teams.}
    \end{cvitems}
    }

\cventry
    {Technology Lead}
    {\href{https://www.evidasolve.com/mosaycity}{EvidaSolve: moSAYcity}}
    {Virtual}
    {December 2021 - December 2022}
    {
    \begin{cvitems}
       \item {Led the development of a scalable cloud-based app to connect individuals within large organizations.}
       \item {With EvidaSolve founder Shalini Nag, pitched moSAYcity at the Reverse Pitch Competition MKE and won first prize. Selected for an additional prize in the community showcase.}
    \end{cvitems}
    }

\cventry
    {Postdoctoral Fellow}
    {\href{https://morgridge.org/}{Morgridge Institute for Research} / University of Wisconsin - Madison}
    {Madison, WI}
    {October 2019 - October 2022}
    {
    \begin{cvitems}
       \item {Co-Advisor: \href{https://anantharamanlab.com/}{Karthik Anantharaman}, Department of Bacteriology}
       \item {Co-Advisor: \href{https://www.biostat.wisc.edu/~gitter/}{Anthony Gitter}, Morgridge Institute for Research}
       \item {Applied complexity measurements and analysis to protein-protein interactions between Influenza-A and humans.}
    \end{cvitems}
    }

\cvsubposition
    {\href{http://www.cibm.wisc.edu/}{CIBM Postdoctoral Trainee}}
    {October 2019 - October 2021}
    {
    \begin{cvitems}
       \item {Advisor: \href{https://anantharamanlab.com/}{Karthik Anantharaman}, Department of Bacteriology, Co-Advisor: Federico Rey, Department of Bacteriology}
       \item {Funding: Computation and Informatics in Biology and Medicine Training Program (NLM 5T15LM007359)}
       \item {Used -omics data, complexity theory, and computation theory to understand how different microbial communities interact with one another.}
       \item {Investigated protein-protein interactions between phages and bacteria in microbial communities.}
       \item {Developed high-speed software solutions for measuring complexity, entropy, and information within -omics data.}
    \end{cvitems}
    }

\cventry
    {Director}
    {\href{https://vedadata.com/}{VEDA Data Solutions}}
    {Madison, WI}
    {August 2017 - September 2019}
    {
    \begin{cvitems}
       \item {Oversaw and managed Labs research projects, communicated across departments to coordinate and allocate project resources.}
       \item {Mentored and guided research fellows on projects resulting in scientific discoveries, products, or enhancements.}
       \item {Fostered connections with academic institutions and managed external collaborations.}
    \end{cvitems}
    }

\cvsubposition
    {Data Scientist}
    {August 2017 - September 2019}
    {
    \begin{cvitems}
       \item {End-to-end data pipeline development, from data collection and engineering, to data analysis and visualization using Python and SQL.}
       \item {Developed and scaled backend software products customized to client-specific needs.}
       \item {Built and maintained data processing systems that processed over 100 million rows of data every 24 hours.}
       \item {Performed regular data Q\&A monitoring to ensure data health and accuracy, and identify improvement areas.}
    \end{cvitems}
    }

\cventry
    {Co-Developer and Teaching Assistant}
    {Santa Fe Institute: Complexity Explorer}
    {Remote}
    {May 2018 - September 2018}
    {
    \begin{cvitems}
       \item {Course name: \href{https://www.complexityexplorer.org/courses/63-algorithmic-information-dynamics-a-computational-approach-to-causality-and-living-systems-from-networks-to-cells}{Algorithmic Information Dynamics: A Computational Approach to Causality and Living Systems From Networks to Cells}}
       \item {Co-developed course content, assisted with student learning, and led research projects with students.}
    \end{cvitems}
    }

\cventry
    {Intern}
    {Microsoft Research}
    {Cambridge, UK}
    {Summer 2017}
    {
    \begin{cvitems}
       \item {Supervisor: Katja Hofmann}
       \item {\href{https://www.microsoft.com/en-us/research/project/project-malmo/}{Project Malm\"{o}} team: Developed a sophisticated AI experimentation platform as an extension of Minecraft}
       \item {Implemented new machine learning techniques: Reinforcement learning, one-shot imitation learning, deep-Q architecture, LSTMs.}
       \item {Built a two-player game between a human player and a one-shot imitation learning agent, demonstrating open-ended imitation learning in a system coupled with an open-ended human player.}
    \end{cvitems}
    }

\cventry
    {Research Assistant}
    {Beyond Center, \href{http://emergence.asu.edu/}{Emergence Lab}}
    {Arizona State University}
    {August 2014 - May 2017}
    {
    \begin{cvitems}
        \item {Funding: John Templeton World Charity Foundation}
        \item {Used cellular automata to study mechanisms that lead to open-ended dynamics.}
        \item {Developed a new metric to quantify open-endedness in discrete, bounded, and synchronously-updating dynamical systems.}
        \item {Studied philosophy of complexity, emergence, and intelligence to re-define the question "What is life?"}
        \item {Used data produced in online video games to explore questions related to complexity and emergence.}
    \end{cvitems}
    }

\cventry
    {Teaching Assistant}
    {Department of Physics}
    {Arizona State University}
    {August 2013 - May 2014}
    {
    \begin{cvitems}
        \item {Course name: Physics 101}
        \item {Assisted with student learning by holding weekly study sessions, giving quizzes and homework, grading, and holding additional study sessions before exams.}
    \end{cvitems}
    }

\cventry
    {Research Assistant}
    {East Tennessee State University}
    {Johnson City, TN}
    {January 2011 - May 2012}
    {
    \begin{cvitems}
        \item {Supervisor: Frank B. Hagelberg}
        \item {Explored the use of potassium ferrocyanide nanoparticles as an energy-efficient component in solar cells.}
        \item {Learned computational modeling techniques for nanoscale materials research.}
    \end{cvitems}
    }

\end{cventries}
