\cvsection{Workshops}


\begin{cventries}

\cventry
    {Invited Speaker}
    {ALICE Workshop (Artificial Life, Intelligence, Complexity \& Evolution)}
    {Copenhagen, Denmark}
    {Feb. 2026}
    {
    \begin{cvitems}
        \item {Leading discussion groups and facilitating a collaborative project track focused on "Constraints and Functions" in complex systems.}
    \end{cvitems}
    }

\cventry
    {Participant \& Mini-WISE Grant Recipient}
    {Workshop on Integrative Science for Evolution (WISE)}
    {Washington, DC}
    {October 2024}
    {
    \begin{cvitems}
        \item {Selected for an interdisciplinary workshop at the Carnegie Institution for Science, fostering integration across evolutionary biology fields.}
        \item {Awarded a "Mini-WISE" grant to establish and lead a new working group focused on evolutionary constraints.}
        \item {Currently coordinating the working group to finalize a Letter of Intent (LOI) for extended project funding.}
    \end{cvitems}
    }

\cventry
    {Attendee}
    {Open Science Grid Summer School}
    {Madison, WI}
    {Summer 2022}
    {
    \begin{cvitems}
        \item {Learned to use the Open Science Grid computational cluster effectively.}
    \end{cvitems}
    }
    
\cventry
    {ProPhounD Team Representative}{\href{https://d2p.wisc.edu/programs/igniter/}{Igniter}}
    {Madison, WI}
    {Fall 2021}
    {
    \begin{cvitems}
        \item {Learned to implement the Business Model Canvas tool for early startup development.}
       \item {Entrepreneur startup development program aimed at launching an MVP for developing startups.}
       \item {Conducted and reviewed customer discovery interviews to develop ProPhounD's MVP.}
    \end{cvitems}
    }
    
\cventry
    {Attendee}{\href{https://business.wisc.edu/entrepreneurship/morgridge-entrepreneurial-bootcamp/}{Morgridge Entrepreneurial Bootcamp}}
    {Madison, WI}
    {Summer 2021}
    {
    \begin{cvitems}
        \item {Week-long intensive summer course on how to turn an idea into a startup.}
    \end{cvitems}
    }
    
\cventry
    {ProPhounD Team Representative}{\href{https://d2p.wisc.edu/programs/innovation-to-market/}{I2M: Innovation 2 Market}}
    {Madison, WI}
    {Spring 2021}
    {
    \begin{cvitems}
       \item {Entrepreneur startup development program aimed at launching an MVP for developing startups.}
       \item {Conducted and reviewed customer discovery interviews to develop ProPhounD's MVP.}
    \end{cvitems}
    }
    
\cventry
    {Nunus Team Founder}
    {\href{https://www.gener8tor.com/}{gener8tor} CS NEST \& gAPLHA: Social Impact}
    {Madison, WI}
    {Fall 2020 - Spring 2021}
    {
    \begin{cvitems}
       \item {Entrepreneur startup development programs aimed at launching an MVP for developing startups.}
       \item {Founded Nunus as a company dedicated to changing the way users interact with social media.}
       \item {Developed a roadmap and business model to launch an MVP to customers.}
    \end{cvitems}
    }
    
\cventry
    {Attendee}
    {Access Network Assembly}
    {Tempe, AZ}
    {Summer 2016, 2019}
    {
    \begin{cvitems}
       \item {Annual assembly of Access Network Sites from across the nation, including Sundial. Workshop included presentations about diversity and fostering a positive community in the sciences.}
    \end{cvitems}
    }
    
\cventry
    {Scholar}
    {\href{https://astrobiology.nasa.gov/career-funding/astrobiology-summer-school/}{Josep Comas i Sol\`{a} International Summer School in Astrobiology}}
    {Santander, Spain}
    {Summer 2015}
    {
    \begin{cvitems}
       \item {Topic: The Origin of Life, From Monomers to Cells}
       \item {Attended lectures on a variety of perfectives about the origin of life in the universe and participated in a think-tank on how to proceed with important questions in the future.}
    \end{cvitems}
    }
    
\cventry
    {Scholar}
    {\href{https://education.wolfram.com/summer-school}{Wolfram Science Summer School}}
    {Waltham, MA}
    {Summer 2014}
    {
    \begin{cvitems}
       \item {Developed models using cellular automata that explored selection on genomes. Also developed an interacting cellular automata model that is capable of generating open-ended evolution.}
    \end{cvitems}
    }
    
\cventry
    {Participant}
    {Social Justice Summit}
    {Fullerton, CA}
    {2010}
    {
    \begin{cvitems}
       \item {Participated in workshops on gender and language, what it means to be a minority, animal rights/factory farm issues, homelessness, hate crimes and bias, human trafficking, economic injustice and civil disobedience.}
    \end{cvitems}
    }
    
\end{cventries}